\enableregime [utf]

\mainlanguage [en]
\setuppapersize[letter][letter]
\setuppagenumbering[state=off]
\setuphead[section][align={center, nothyphenated, verytolerant},
  textstyle=\sc \tfc]
\setupbodyfont[11pt]
\setupinteraction[state=start,  
  title={Katterhenry-Showalter Wedding Ceremony},
  subtitle={Wedding Ceremony},
  author={Shawn Nock},
  keyword={jason laura wedding katternhenry showalter},
  color=black,
  style=
]
\starttext
\section{Processional}
  %\midaligned{\em /* Wedding party rolls in (looking slick), then Laura (Dress 
  %                   worked out great) */}
\section{Welcome}
  %\midaligned{\em /* Perhaps most importantly, I look awesome. Now I greet some 
  %                   people, on with the show. */}
\blank[big]
Officiant: 
\startnarrower 
  Welcome, family and friends. We gather here today to celebrate the wedding of
  Laura and Jason. You have come here to share in this commitment they make to 
  one another, to offer your love and support to this union, and to allow Laura
  and Jason to start their married life together surrounded by the those most 
  important to them.
  \blank
  Jason and Laura thank you for your presence here today, and now ask for your 
  blessing, encouragement, and lifelong support, for their decision to be 
  married.
  \blank[big]
\stopnarrower
\section{Definition of Marriage}
  %\midaligned{\em /* I, the great dateless wonder, will proceed to school you 
  %                   two on the meaning of marriage.}
  %\midaligned{\em Contrary to popular believe, It's serious business! */}
  \blank[big]
  Officiant: 
  \startnarrower Marriage is perhaps the greatest and most challenging 
  adventure of human relationships. No ceremony can create your marriage; only 
  you can do that – through love and patience; through dedication and 
  perseverance; by talking and listening to each other, by helping, supporting and 
  believing in your spouse's goals; with tenderness and laughter; while learning 
  to forgive and to appreciate your differences. Marriage challenges you to make the
  important things count, 
  and let go of the rest. What this ceremony can do is witness and affirm the 
  choice you make to stand together as 
  lifemates and partners.
  \blank[big]
\stopnarrower

\section{Readings}
  %\midaligned{\em /* Welp, you're in the shit now, I guess we better read some 
  %                   things that people smarter than us wrote...}
  %\midaligned{\em It'll sound fancy! */}
  \blank[big]
  Officiant: 
  \startnarrower Jason and Laura both believe that strong friendships are important to a 
  marriage. With that in mind, they have asked two friends to read a selection about 
  love that resonates with them.
  \stopnarrower
  \blank[big]
  %\midaligned{\sc 1st Reading (Evan)}
  %\midaligned{\em /* I suggest Dr. Suess, he was married... and he fought 
  %                   facism! */}
\page
\startlines
\startalignment[center]
``Oh the Places You'll Go''
by Dr Seuss

Congratulations! Today is your day.
You're off to Great Places! You're off and away!
You have brains in your head. You have feet in your shoes.
You can steer yourself any direction you choose.
You're on your own. And you know what you know.
And YOU are the couple who'll decide where to go.
You'll look up and down streets. Look 'em over with care.
About some you will say,``We don't choose to go there.''
With your heads full of brains and your shoes full of feet,
You're too smart to go down, any not-so-good street.
And you may not find any you'll want to go down.
In that case, of course, you'll head straight out of town.
It's opener there in the wide open air,
Out there things can happen and frequently do
to people as brainy and footsy as you.
And when things start to happen, don't worry. Don't stew.
Just go right along. You'll start happening too.
%\stopalignment
%\stoplines
%\midaligned{\sc 2nd Reading (Anne)}
%\startlines
%\startalignment[center]

OH! THE PLACES YOU'LL GO!

You'll be on your way up! You'll be seeing great sights!
You'll join the high fliers who soar to great heights!
You won't lag behind, because you'll have all the speed.
You'll pass the whole gang, and you'll soon take the lead.
Wherever you fly you'll be best of the best.
Wherever you go, you will top all the rest.
Except when you don't. Because sometimes, you won't.
You'll get mixed up of course, as you already know.
You'll get mixed up with so many strange birds as you go.
So be sure when you step.
Step with great care and great tact
and remember that Life's a Great Balancing Act.
Just never forget to be dexterous and deft.
And never mix up your right foot with your left.
And will you succeed?
Yes! You will indeed!
98 and 3/4 percent guaranteed.
\stopalignment
\stoplines
  \blank[big]
  %\midaligned{\em /* What? You think you can do better? */}
 \section{Declaration of Intent}
  %\midaligned{\em /* Do you? How 'bout you? Last chance to pull the eject 
  %                   handle. */}
  \blank[big]
  Officiant: 
  \startnarrower Laura and Jason will now declare their intent to be married.
  Will you, Jason, take Laura to be your wedded wife?
  \stopnarrower
  Jason: 
  \startnarrower I will
  \stopnarrower
  Officiant: 
  \startnarrower Will you, Laura, take Jason to be your wedded husband?
  \stopnarrower
  Laura:
  \startnarrower I will
  \stopnarrower
  \blank[big] %\blank[big]
\section{Wedding Vows}
  %\midaligned{\em /* Really big show, really big! */}
  Officiant: 
  \startnarrower We've come to the point of your ceremony where you're going 
  to say your vows to one another. But before you do that, I ask you to 
  remember that love – which is rooted in faith, trust, and acceptance - will 
  be the foundation of an abiding and deepening relationship. No other ties 
  are more tender, no other vows more sacred than those you now assume. If you 
  are able to keep the vows you take here today, not because of any religious 
  or civic law, but out of a desire to love and be loved by another person 
  fully, without limitation, then your life will have joy and the home you 
  establish will be a place in which you both will find the direction of your 
  growth, your freedom, and your responsibility.
  \stopnarrower
  Officiant:
  \startnarrower Please read the vows you have written for each other.
  \stopnarrower
  %\midaligned{\em /* Love, cherish, respect, blah... blah... blah... */}
  Laura:
  \startnarrower
  Jason,

	For the last five and a half years, you have been an incredible force in my life. You are my best friend, my confidante, my strongest supporter, and the person I can’t wait to spend the rest of my life with. In that time I promise to stand by your side as together we face the challenges of life, and share the joy of living. I will take care of you when you’re sick, comfort you when you’re sad, and laugh with you every day. I promise to always be there for you when you need my most. If life’s got you down and you just need a hug, I’ll be there. If you want to sit around in your pajamas on a Sunday and play video games all day, I’ll be there. If you want to fall asleep next to someone while watching QVC in bed, I’ll be there. And if you want someone to love you for the rest of your life, I’m here. I love you, Jason.
\stopnarrower
\page
Jason:
\startnarrower
Laura,

Five years ago you sent me a letter with the key to your heart,
each day since then you have become even more my friend,
someone to laugh with, count on, and especially, love.
There is no one else I would rather spend eatch coming day with.
Five years ago you sent me a letter with the key to your heart,
today in return I promise you my eternal friendship, support, and love.
\stopnarrower  

  Officiant: 
  \startnarrower May we have the rings, please?
  \stopnarrower
  Officiant:
  \startnarrower Laura, Please repeat after me: {\em I give you this ring, as a daily 
    reminder of my love for you.}
  \stopnarrower
  Laura:
  \startnarrower I give you this ring, as a daily reminder of my love for you.
  \stopnarrower
  Officiant:
  \startnarrower Jason, Please repeat after me: {\em I give you this ring, as a daily 
    reminder of my love for you.}
  \stopnarrower
  Jason:
  \startnarrower I give you this ring, as a daily reminder of my love for you.
  \stopnarrower
  Officiant: 
  \startnarrower By the power of your love and commitment
  I now pronounce you husband and 
  wife! You may kiss each other!
  \stopnarrower
  \blank[big]
\section{Recessional}
  %\midaligned{\em /* Und now I drink! Also, I hit on all your single female 
  % friends}
  %\midaligned{\em (and possibly the married ones... I will be drinking after 
  %  all). */}

\stoptext

